Automated Verification of Stand-alone Solar Photovoltaic Systems: Optimal Sizing and Project Validation

### 2019-10-28 Tex/Old text/chapters/conclusion.tex
tweaks
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

At this final chapter, we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were used to tackle solar PV systems issues, as validation over time and sizing optimization. Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources) closes the work.

>>>>

Here we present the conclusions about the research done and the results obtained during the Doctoral process, including the two scientific methods or techniques from computer science that were used to tackle solar PV systems issues, as validation over time and sizing optimization. Moreover, a list of future contributions, which probably will foster the creation of a research group that applies model checking to electrical systems (not only renewable sources) closes the work.
